Delocalization of Eigenvectors in Random Matrices

### 2025-03-20 Draft.tex
typos

\noindent The particular delocalization bound for $W \gg N^{8/11}$ emerges from the need of ensuring that the combined error term $W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$ in equation $(3.2.1)$ is much smaller than the typical size of the $\Theta$ entries of $O( W^{-1}\eta^{-\frac{1}{2}})$, while maintaining he diffusion time scale $\eta \approx W^2N^{-2}$ (\hyperref[diffusion]{Sec. 4.1}) :

$$W^{-\frac{7}{4}}\eta^{-\frac{3}{2}} \ll W^{-1}\eta^{-\frac{1}{2}}$$

$$W^{-\frac{7}{4}}(W^2N^{-2})^{-\frac{3}{2}} \ll W^{-1}(W^2N^{-2})^{-\frac{1}{2}}$$

$$\Rightarrow W^{-\frac{7}{4}}W^{-3}N^3 \ll W^{-1}W^{-1}N$$
$$\quad W^{-\frac{11}{4}} \ll N^{-2}\quad\Leftrightarrow W \gg N^{\frac{8}{11}}$$

@@

\textbf{Lemma A2} \label{lemma-a2}

>>>>

\noindent The particular delocalization bound for $W \gg N^{8/11}$ emerges from the need for the combined error term $W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$ in equation $(3.2.1)$ to be much smaller than the typical size of the $\Theta$ entries of $O( W^{-1}\eta^{-\frac{1}{2}})$, while maintaining he diffusion time scale $\eta \approx W^2N^{-2}$ (\hyperref[diffusion]{Sec. 4.1}) :

$$W^{-\frac{7}{4}}\eta^{-\frac{3}{2}} \ll W^{-1}\eta^{-\frac{1}{2}}$$
$$W^{-\frac{7}{4}}(W^2N^{-2})^{-\frac{3}{2}} \ll W^{-1}(W^2N^{-2})^{-\frac{1}{2}}$$
$$\Rightarrow W^{-\frac{7}{4}}W^{-3}N^3 \ll W^{-1}W^{-1}N$$
$$\quad W^{-\frac{11}{4}} \ll N^{-2}\quad\Leftrightarrow W \gg N^{\frac{8}{11}}$$

@@

\textbf{Lemma A2} \label{lemma-a2} - Lemma 23
